Measuring individual differences in the understanding of gaze cues

### 2022-09-02 paper/manuscript.Rmd
incorporate Daniel's feedback; pre-registration deviations; participant exclusions

---
title             : "TANGO: A reliable, open-source, web-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults"
shorttitle        : "assessing individual differences in gaze understanding"
author:

@@

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
authornote: |
abstract: |
  Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals. 
  Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief(approx. 5-10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues. 
   Our interactive browser-based task works across devices and enables in-person and remote testing. The implemented spatial layout allows for discrete and continuous measures of participants’ click imprecision and is easily adaptable to different study requirements. 
   Our task induces inter-individual differences in a child (N = 387) and an adult (N = 236) sample. Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target. High internal consistency and test-retest reliability estimates underline that the captured variation is systematic. This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the in(ter)dependence of our core social-cognitive processes in greater detail.
  All materials and code are freely accessible to interested researchers. A version of the task is accessible online: https://ccp-odc.eva.mpg.de/tango-demo/.

keywords          : "social cognition, individual differences, gaze cues, cognitive development"
wordcount         : "6705"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

Numerous studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya]. These individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcome [for an overview, see @repacholi2003introduction]. Studies on social-cognitive abilities and family influences include the effect of parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background as parental education, occupation, sibling interaction and childcare [@dunn1991young; @cutting1999theory; @bulgarelli2016social]. Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins]. Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].

@@

However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction]. Thus, this task seems well suited to track group-level developmental trends, yet it fails to capture individual differences [cf. "reliability paradox", @hedge2018reliability].
As @wellman2012theory put it, "it's really only passing/failing one sort of understanding averaged across age" (p. 317).
This has profound implications for what studies on individual differences using this task (or others) can show.
Poor measurement of social cognition on an individual level is likely to conceal relations between different aspects of cognition and may obscure developmental change.

Thus, developmental psychology faces a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to measure these individual differences reliably.
To capture the emergence of social-cognitive abilities and related social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs [@hughes2004links; @hughes2011individual].

@schaafsma2015deconstructing compiled a "wish list" for new social-cognitive paradigms.
They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates [see also @beaudoin2020systematic; @hughes2015individual].
New tasks should induce variation across age groups, including older children and adults [@repacholi2003introduction].
Another goal in creating new tasks should be to focus on the "face value": measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical, and demographic contexts [@molleman2019unleashing].
The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences [@repacholi2003introduction].

@@

The web app was programmed in `JavaScript`, `HTML5`, `CSS` and `PHP`.
For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
This way, the composition scales according to the user's viewport without loss of quality while keeping the aspect ratio and relative object positions constant.
Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
This is needed for precisely calculating exact pupil and target locations and sizes.
Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
The web app generates two file types: (1) a text file (.json) containing meta-data, trial specifications, and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
These files can either be sent to a server or downloaded to the local device.
Personalized links can be created by passing on URL parameters.

@@

To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects.
Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130%) and change in opacity (decrease to 75%) for 0.3 sec.
The landing of the target is accompanied by a tapping sound.
Once the target landed, the instructor's voice asks "Where is the balloon?".
For confirming the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
Participants do not receive differential feedback so that learning effects are reduced, and trials stay comparable across the sample.
If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.

@@

(ref:figlab1) **Study setup**. (A) Infrastructure for online testing. (i) Subjects aged 3 -- 99+ can participate. Data collection can take place anywhere: online, in kindergartens, or research labs. (ii) The task is presented as a website that works across devices. (iii) The scripts for the website and the recorded data are stored on secure local servers. (B) Hedge version (continuous) of the TANGO. (i) The agent stands in a window with the target in front of them. (ii) A hedge grows and covers the target. (iii) The target falls to a random location on the ground. The agent's eyes track the movement of the target. (C) Box version (discrete) of the TANGO. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.

@@

Our first aim was to assess whether the TANGO induces inter-individual variation in a child and adult sample.
Furthermore, we were interested in how the data collection mode (in-person vs. remote) influences responses.

Methods, sample size, and analysis were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
Participants were equally distributed across the two study versions.
The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
Data was collected between May and October 2021.

@@

For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in child development studies and who indicated an interest in online studies.
Families received an email with a short study description and a personalized link.
If they had not participated in the study within two weeks, they received a reminder via email.
Response rate to invitations after the reminder was \~50%.

The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls), `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls), and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls).
Children in our sample grow up in an industrialized, urban Central-European context.
Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.

Adults were recruited via *Prolific* [@palan2018prolific].
*Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females).
For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).

@@

Children in the remote sample received a personalized link to the study website, and families could participate at any time or location.
At the beginning of the online study, families were invited to enter our "virtual institute".
We welcomed them with a short introductory video of the study leader, describing the research background and further procedure.
Then, caregivers were informed about data security and were asked for their informed consent.
They were asked to enable the sound and seat their child centrally in front of their device.
Before the study started, families were instructed how to setup their webcam and enable the recording permissions.
We stressed that caregivers should not help their children.
Study participation was video recorded whenever possible in order to ensure that children themselves generated the answers.
Depending on the participant's device, the website automatically presented the hedge or box version of the study.
For families that used a tablet with touchscreen, the hedge version was shown.
Here, children could directly click on the touchscreen to indicate where the target is.
For families that used a computer without touchscreen, the website presented the box version of the task.
We assumed that younger children in our sample would not be acquainted with using a computer mouse.
Therefore, we asked children to point to the screen, while caregivers were asked to act as the "digital finger" of their children and click on the indicated box.

@@

All test trials without voice-over description were included in our analyses.
We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].

@@

(ref:figlab2) **Measuring inter-individual variation**. (A) Developmental trajectory in continuous hedge version. Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials). The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center. (B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample. (F) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes). (G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample. For (A) and (F), regression lines show the predicted developmental trajectories (with 95% CrI) based on GLMMs, with the line type indicating the data collection mode. For (B-E) and (G-J), regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*. Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). Small points show the mean performance for each subject averaged across trials. Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds for remote unsupervised data collection. Color of data points denotes age group.

@@

We found a strong developmental effect: with increasing age, participants got more accurate in locating the target.
In the hedge version, children's click imprecision decreased with age, while in the box version the proportion of correct responses increased (see Figure \@ref(fig:fig2)A and F).
Most participants in the box version performed above chance level.
By the end of their sixth year of life, children came close to the adult's proficiency level.
Most importantly, however, we found substantial inter-individual variation across study versions and age groups.
For example, some three-year-olds were more precise in their responses than some five-year-olds.
Even though variation is smaller, we could even find inter-individual differences in the adult sample.

@@

Our task induced inter-individual variation in both children and adults.
We see substantial developmental gains: with increasing age, participants became more and more precise in locating the target.
The five-year-olds reached a proficiency level close to the adults' level.
For neither study version nor age group did we find any floor or ceiling effects.
The presentation as a web-app with cartoon-like features kept children interested and motivated throughout the 15 test trials.
Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
This illustrates the flexibility of the task design.

@@

As a next step, we aimed to investigate whether the variation that we captured with the TANGO is reliable.
We assessed internal consistency (as split-half reliability) and test-retest reliability.
Data collection and analysis were pre-registered (<https://osf.io/xqm73> for the child sample and <https://osf.io/nu62m> for the adult sample).
Participants were equally distributed across the two study versions.
The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
Data was collected between July 2021 and June 2022.

@@

The adult sample consisted of `r reli_adults$nTotal` English-speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females).

@@

We applied the same procedure as in the first study, with the following differences.
Participants completed the study twice, with a delay of 14 ± 3 days.
The target locations, as well as the succession of agents and target colors, were randomized once and then held constant across participants.
The child sample received 15 test trials.
In the hedge version, each bin occurred once, making up ten of the test trials.
For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 & 2, bin 3 & 4, etc.).
In the box version, we ensured that each of the five boxes occurred exactly three times during test trials.
Adults in the hedge version received 30 test trials, each of the ten bin occurring exactly three times.
Adults in the box version received 32 test trials, with each of the eight boxes occurring exactly four times.
For the four training trials, we repeated a fixed order of random bins/boxes.

@@

We assessed reliability in two ways.
First, we focused on internal consistency by calculating split-half reliability coefficients.
For each subject, trials were split into odd and even trials, performance was aggregated and then correlated using *Pearson* coefficients.
For this, we used the data of the first test day.
Performance was defined according to each study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.

@@

We found that the TANGO induced systematic variation: split-half and test-retest reliability was medium to high.
For internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)B, C, G, and H.

@@

>>>>

---
title             : "TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults"
shorttitle        : "assessing individual differences in gaze understanding"
author:

@@

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
authornote: |
abstract: |
  Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals. 
  Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx. 5-10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues. 
   Our interactive browser-based task works across devices and enables in-person and remote testing. The implemented spatial layout allows for discrete and continuous measures of participants’ click imprecision and is easily adaptable to different study requirements. 
   Our task measures inter-individual differences in a child (N = 387) and an adult (N = 236) sample. Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target. High internal consistency and test-retest reliability estimates underline that the captured variation is systematic. This work shows a promising way forward in the study of individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.

keywords          : "social cognition, individual differences, gaze cues, cognitive development"
wordcount         : "6859"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

Numerous studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya]. These individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcome [for an overview, see @repacholi2003introduction]. Studies on social-cognitive abilities and family influences include the effect of parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background as parental education, occupation, sibling interaction and childcare [@dunn1991young; @cutting1999theory; @bulgarelli2016social]. Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins]. Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes, and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].

@@

However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction]. Thus, this task seems well suited to track a particular group-level developmental transition, yet it fails to capture individual differences [cf. "reliability paradox", @hedge2018reliability].
As @wellman2012theory put it, "it's really only passing/failing one sort of understanding averaged across age" (p. 317).
This has profound implications for what studies on individual differences using this task (or others) can show.
Poor measurement of social cognition on an individual level is likely to conceal relations between different aspects of cognition and may obscure developmental change.

Thus, developmental psychology faces a dilemma: many research questions rely on measuring individuals' development, yet, there is a lack of tasks to measure these individual differences reliably.
To capture the emergence of social-cognitive abilities and their relation to social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs [@hughes2004links; @hughes2011individual].

@schaafsma2015deconstructing compiled a "wish list" for new social-cognitive paradigms.
They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates [see also @beaudoin2020systematic; @hughes2015individual].
New tasks should capture variation across age groups, including older children and adults [@repacholi2003introduction].
Another goal in creating new tasks should be to focus on the "face value": measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical, and demographic contexts [@molleman2019unleashing].
The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences [@repacholi2003introduction].

@@

The web app was programmed in `JavaScript`, `HTML5`, `CSS,` and `PHP`.
For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
This way, the composition scales according to the user's viewport without loss of quality while keeping the aspect ratio and relative object positions constant.
Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
This is needed for precisely calculating the exact pupil and target locations and sizes.
Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
The web app generates two file types: (1) a text file (.json) containing meta-data, trial specifications, and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
These files can either be sent to a server or downloaded to the local device.
Personalized links can be created by passing on URL parameters.

@@

To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects.
Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130%) and change in opacity (decrease to 75%) for 0.3 sec.
The landing of the target is accompanied by a tapping sound.
Once the target landed, the instructor's voice asked "Where is the balloon?".
To confirm the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
Participants do not receive differential feedback, so that learning effects are reduced, and trials stay comparable across the sample.
If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.

@@

(ref:figlab1) **Study setup**. (A) Infrastructure for online testing. (i) Subjects aged 3 -- 99+ can participate. Data collection can take place anywhere: online, in kindergartens, or in research labs. (ii) The task is presented as a website that works across devices. (iii) The scripts for the website and the recorded data are stored on secure local servers. (B) Hedge version (continuous) of the TANGO. (i) The agent stands in a window with the target in front of them. (ii) A hedge grows and covers the target. (iii) The target falls to a random location on the ground. The agent's eyes track the movement of the target. (C) Box version (discrete) of the TANGO. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.

@@

Our first aim was to assess whether the TANGO captures inter-individual variation in a child and adult sample.
Furthermore, we were interested in how the data collection mode (in-person vs. remote) influences responses.

Task design, data collection, and sample sizes were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations.
The additional analyses mentioned in the pre-registrations (e.g., computational model) will be reported elsewhere.

The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl. No. 2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
The research adheres to the legal requirements of psychological research with children in Germany.

Participants were equally distributed across the two study versions.
Data were collected between May and October 2021.

@@

We pre-registered the replacement for participants that finished fewer than four test trials.
This was not the case for any participant.
One child stopped participation after 16 trials (i.e., 3 test trials missing) but was included in the sample due to the pre-registered replacement rule.
Two additional participants were recruited but not included in the study because the participant did not feel comfortable interacting with the tablet alone (n = 1), or due to an originally miscalculated age of the child (n = 1).

For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in child development studies and who indicated an interest in online studies.
Families received an email with a short study description and a personalized link.
If they had not participated in the study within two weeks, they received a reminder via email.
The response rate to invitations after the reminder was \~50%.

The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls), `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls), and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls).
Of these, three families participated twice.
In these cases, we only kept the data sets from the first participation.

Four additional participants were recruited but not included in the study because they were already part of the in-person kindergarten sample (n=3), or because of unknown age (n = 1).

Children in our sample grow up in an industrialized, urban Central-European context.
Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.

Adults were recruited via *Prolific* [@palan2018prolific].
*Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
`r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females) were included.
For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).

@@

Children in the remote sample received a personalized link to the study website, and families could participate at any time or location.
At the beginning of the online study, families were invited to enter our "virtual institute".
We welcomed them with a short introductory video of the study leader, describing the research background and further procedure.
Then, caregivers were informed about data security and were asked for their informed consent.
They were asked to enable the sound and seat their child centrally in front of their device.
Before the study started, families were instructed on how to set up their webcam and enable the recording permissions.
We stressed that caregivers should not help their children.
Study participation was video recorded whenever possible in order to ensure that the children themselves generated the answers.
Depending on the participant's device, the website automatically presented the hedge or box version of the study.
For families that used a tablet with a touchscreen, the hedge version was shown.
Here, children could directly click on the touchscreen to indicate where the target is.
For families that used a computer without a touchscreen, the website presented the box version of the task.
We assumed that younger children in our sample would not be acquainted with using a computer mouse.
Therefore, we asked children to point to the screen, while caregivers were asked to act as the "digital finger" of their children and click on the indicated box.

@@

All test trials without voice-over descriptions were included in our analyses.
We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].

@@

(ref:figlab2) **Measuring inter-individual variation**. (A) Developmental trajectory in the continuous hedge version. Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials). The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center. (B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample. (F) Developmental trajectory in the discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target. The dotted black line shows the level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes). (G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample. For (A) and (F), regression lines show the predicted developmental trajectories (with 95% CrI) based on GLMMs, with the line type indicating the data collection mode. For (B-E) and (G-J), regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*. Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). Small points show the mean performance for each subject averaged across trials. The shape of data points represents data collection mode: opaque circles for in-person supervised data collection and translucent diamonds for remote unsupervised data collection. the color of data points denotes age group.

@@

We found a strong developmental effect: with increasing age, participants got more accurate in locating the target.
In the hedge version, children's click imprecision decreased with age, while in the box version, the proportion of correct responses increased (see Figure \@ref(fig:fig2)A and F).
Most participants in the box version performed above chance level.
By the end of their sixth year of life, children came close to the adult's proficiency level.
Most importantly, however, we found substantial inter-individual variation across study versions and age groups.
For example, some three-year-olds were more precise in their responses than some five-year-olds.
Even though variation is smaller, we could even find inter-individual differences in the adult sample.

@@

Our task measured inter-individual variation in both children and adults.
We see substantial developmental gains: with increasing age, participants became more and more precise in locating the target.
The five-year-olds reached a proficiency level close to the adults' level.
For neither study version nor age group did we find any floor or ceiling effects.
The presentation as a web-app with cartoon-like features kept children interested and motivated throughout the 15 test trials.
Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
This illustrates the flexibility of the task design.

@@

As a next step, we aimed to investigate whether the variation that we captured with the TANGO is reliable.
We assessed internal consistency (as split-half reliability) and test-retest reliability.
Task procedure, data collection, and sample sizes were pre-registered (<https://osf.io/xqm73> for the child sample and <https://osf.io/nu62m> for the adult sample).
Participants were equally distributed across the two study versions.
Data was collected between July 2021 and June 2022.

The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl. No. 2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
The research adheres to the legal requirements of psychological research with children in Germany.

@@

Additional 65 children were recruited but not included in the analysis due to absence on the second test day (n = 49), canceled testing because of Covid cases in the kindergarten (n = 7), children did not want to participate a second time (n = 5), children already participated in the first data collection round and were included in the above-mentioned *Individual Differences* sample (n = 3), or children did not understand the task instructions (n = 1).
Two additional children were recruited for the first day (as backup) in case another child would be absent on the second test day.

The adult sample included `r reli_adults$nTotal` English speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females; see Supplements for further details).

@@

We applied the same procedure as in the first study, with the following differences.
Participants completed the study twice, with a delay of 14 ± 3 days.
The target locations, as well as the succession of agents and target colors, were randomized once and then held constant across participants.
The child sample received 15 test trials.
In the hedge version, each bin occurred once, making up ten of the test trials.
For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bins 1 & 2, bins 3 & 4, etc.).
In the box version, we ensured that each of the five boxes occurred exactly three times during test trials.
Adults in the hedge version received 30 test trials, each of the ten bins occurring exactly three times.
Adults in the box version received 32 test trials, with each of the eight boxes occurring exactly four times.
For the four training trials, we repeated a fixed order of random bins/boxes.

@@

We assessed reliability in two ways.
First, we focused on internal consistency by calculating split-half reliability coefficients.
For each subject, trials were split into odd and even trials.
Performance was aggregated and then correlated using *Pearson* coefficients.
For this, we used the data of the first test day.
Performance was defined according to each study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.

@@

We found that the TANGO measured systematic variation: split-half and test-retest reliability was medium to high.
For internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)B, C, G, and H.

@@

For both study versions, reliability estimates based on the GLMM approach were higher than the *Pearson* correlations.
The GLMM-based estimates are less noisy due to the fact that the model uses all available information (e.g., participant age) and does not rely on data aggregation across trials.
